Multi-scale assessment of a grassland productivity model

### 2020-12-27 manuscript/manuscript.Rmd
new 2nd paragraph in intro

There are several potential limitations in the underlying productivity models which can drive such a projection. Process-based models parameterized with observed data have limited transferability beyond the spatial scale from which their training data came [@taylor2019a]. For any location the most accurate model will be one which was parameterized from locally collected data, yet these site-specific models will not generalize to new locations [@basler2016]. Incorporating more, and diverse, locations into the model building process will allow it to be more generalizable, yet this comes at a cost of decreased proficiency at all locations [@garcia-mozo2008; @basler2016]. Thus there is an optimal scale in the building and subsequent application of productivity models, which depends on a tradeoff between proficiency at the local scale and applicability at the larger scale.

Here we evaluate a productivity model with the intention of it driving long-term projections. The PhenoGrass model developed by @hufkens2016 is a pulse-response productivity model with temperature and precipitation as the primary drivers. The model is parameterized using observations from the PhenoCam network, which have a small spatial resolution  (footprints of < 1ha), sub-daily sampling and sites across all major biomes. These attributes make the PhenoGrass model potentially widely applicable. We expand on the evaluation of the original study by using 84 PhenoCam sites, totalling 89 distinct time series, with 463 site-years of data. We test the model’s performance across varying combinations of North American ecoregions and vegetation types to find an optimal spatial scale in which to parameterize and apply the model. Finally we address where the model performs poorly and how productivity projections for these areas could be implemented or improved.

>>>>

A promising method is low dimensional models, which are process models with some simplified components [@choler2010; @choler2011]. For example, a low dimensional model might approximate transpiration to a function of potential evapotranspiration, soil available water, and live vegetation cover along with a single parameter. As opposed to a high dimensional model with multiple functions accounting for leaf area index, stomatal conductance, rooting depth and surface area, etc [@caylor2009; @asbjornsen2011]. The low dimensional model is advantageous since it can generalize across broad regions with relatively few inputs. Yet they are still susceptible to over-fitting to local conditions since parameters or model structure can be tied to specific locations or plant functional groups [@fisher2020]. Thus parameterizing low-dimensional models must be done with care such that they are applicable to a broad area while maintaining an acceptable level of accuracy.

Here we evaluate a low-dimensional model with the intention of it driving productivity projections. The PhenoGrass model developed by @hufkens2016 is a pulse-response productivity model with temperature and precipitation as the primary drivers. The model is parameterized using observations from the PhenoCam network, which have a small spatial resolution  (footprints of < 1ha), sub-daily sampling and sites across all major biomes. These attributes make the PhenoGrass model potentially widely applicable. We expand on the evaluation of the original study by using 84 PhenoCam sites, totalling 89 distinct time series, with 463 site-years of data. We test the model’s performance across varying combinations of North American ecoregions and vegetation types to find an optimal spatial scale in which to parameterize and apply the model. Finally we address where the model performs poorly and how productivity projections for these areas could be implemented or improved.
